---
title: "Plotly"
author: "Amelia Zhao"
date: "10/31/2019"
output: 
  flexdashboard::flex_dashboard:
    orientation:columns
    vertical_layout:fill
---

This dashboard examines the NYC Department of Health and Mental Hygiene (DOHMH) restaurant inspections up to October 2017. The source data, including updated data, can be found [here](https://dev.socrata.com/foundry/data.cityofnewyork.us/43nn-pn8j). 


The restaurants examined are on my personal list of restaurants that I would like to visit, but have not been to. It is a small sample of 11 different restaurants, including some chain restaurants with multiple locations. Luckily, none of these restaurants had any public health hazard violations!


```{r setup, include = FALSE}
library(tidyverse)
library(p8105.datasets)
library(plotly)
library(flexdashboard)
data("rest_inspec")
```


Column {data-width=650}
-----------------------------------------------------------------------

### Distribution of Inspection Scores by Cuisine Type

```{r}
fooddata <-
  rest_inspec %>% 
  filter(
    dba %in% c("HAKKASAN", "CHO DANG GOL", "WONDEE SIAM", "PICCOLA CUCINA", "ADRIENNE'S PIZZA BAR", "RIBALTA", "LOS TACOS NO.1", "SOPHIE'S CUBAN CUISINE", "KEENS STEAKHOUSE", "JONGRO BBQ", "L'AMICO/THE VINE"),
    !is.na(score)) 
    
fooddata %>% 
  plot_ly(y = ~score, color = ~cuisine_description, type = "box") %>% 
  layout(yaxis = list(title = 'Score'), xaxis = list(title = 'Type of Cuisine')) %>% 
  layout(title = "Scores by Cuisine Type")
```

Column {data-width=350}
-----------------------------------------------------------------------

### Average Inspection Score

```{r}
fooddata %>%
  group_by(dba) %>% 
  select(dba, score) %>% 
  summarise(score_mean = mean(score)) %>% 
  plot_ly(x = ~dba, y = ~score_mean, type = "bar") %>%
  layout(yaxis = list(title = 'Mean Score'), barmode = 'stack', xaxis = list(title = 'Restaurant Name')) %>% 
  layout(title = "Average Inspection Scores for Each Restaurant on Amelia's List")
```

### Restaurant or Chain's Inspection Scores over Time

```{r}

fooddata %>% 
  plot_ly(x = ~inspection_date, y = ~score, color = ~dba) %>% 
  add_lines() %>% 
  layout(yaxis = list(title = 'Score'), barmode = 'stack', xaxis = list(title = 'Restaurant Name')) %>% 
  layout(title = "Restaurant/Chain Score over Time")

```




