---
title: "Plotly"
author: "Amelia Zhao"
date: "10/31/2019"
output: 
  flexdashboard::flex_dashboard:
    orientation:columns
    vertical_layout:fill
---

This dashboard examines the NYC Department of Health and Mental Hygiene (DOHMH) restaurant inspections up to October 2017. The source data, including updated data, can be found [here](https://dev.socrata.com/foundry/data.cityofnewyork.us/43nn-pn8j). 


The restaurants examined are on my personal list of restaurants that I would like to visit, but have not been to. It is a small sample of 10 different restaurants, including some chain restaurants with multiple locations. Luckily, none of these restaurants had any public health hazard violations!


```{r setup, include = FALSE}
library(tidyverse)
library(p8105.datasets)
library(plotly)
library(flexdashboard)
data("rest_inspec")
```


Column {data-width=650}
-----------------------------------------------------------------------


### Restaurant or Chain's Inspection Scores over Time
This line graph shows the scores each restaurant received plotted against time. There don't seem to be seasonal/yearly patterns for scores. 


```{r}
fooddata <-
  rest_inspec %>% 
  filter(dba %in% 
           c("HAKKASAN", "CHO DANG GOL", "WONDEE SIAM", "PICCOLA CUCINA", "ADRIENNE'S PIZZA BAR", "RIBALTA", "LOS TACOS NO.1", "SOPHIE'S CUBAN CUISINE", "KEENS STEAKHOUSE", "JONGRO BBQ", "L'AMICO/THE VINE"),
    !is.na(score)) %>% 
  rename(restaurant = dba) %>% 
  mutate(
    cuisine_description = case_when(
      restaurant == "JONGRO BBQ" | restaurant == "CHO DANG GOL" ~ "Korean",
      restaurant == "SOPHIE'S CUBAN CUISINE" ~ "Spanish",
      restaurant == "KEENS STEAKHOUSE" | restaurant ==  "L'AMICO/THE VINE" ~ "American",
      restaurant == "WONDEE SIAM" ~ "Thai",
      restaurant == "HAKKASAN" ~ "Chinese",
      restaurant == "RIBALTA" | restaurant ==  "ADRIENNE'S PIZZA BAR" | restaurant ==  "PICCOLA CUCINA" ~ "Italian"
      )
    )
    
fooddata %>% 
  plot_ly(x = ~inspection_date, y = ~score, color = ~restaurant) %>% 
  add_lines() %>% 
  layout(yaxis = list(title = 'Score'), barmode = 'stack', xaxis = list(title = 'Restaurant Name')) %>% 
  layout(title = "Restaurant/Chain Score over Time")

```


### Distribution of Inspection Scores by Cuisine Type
This box plot shows the distribution of inspection scores for all of the restaurants, stratified by cuisine type. It's difficult to assess a possible relationship between mean scores and type of cuisine since the sample sizes for each cuisine type are very different. 
The cuisine types and corresponding restaurants are categorized as follows: 
American: L'Amico, Keens Steakhouse, 
Chinese: Hakkasan, 
Italian: Ribalta, Adrienne's Pizza Bar, Piccola Cucina, 
Korean: Cho Dang Gol, Jongro BBQ, 
Spanish: Sophie's Cuban, 
Thai: Wondee Siam


```{r}

fooddata %>% 
  plot_ly(y = ~score, color = ~cuisine_description, type = "box") %>% 
  layout(yaxis = list(title = 'Score'), xaxis = list(title = 'Type of Cuisine')) %>% 
  layout(title = "Scores by Cuisine Type")
```

Column {data-width=350}
-----------------------------------------------------------------------

### Average Inspection Score

This bar graph shows the average inspection score for each restaurant/chain. Wondee Siam has the lowest average, which may be due to less inspections occurring there. L'Amico has the highest average, so if I go I will be sure to be careful about what I order...

```{r}
fooddata %>%
  group_by(restaurant) %>% 
  select(restaurant, score) %>% 
  summarise(score_mean = mean(score)) %>% 
  plot_ly(x = ~restaurant, y = ~score_mean, type = "bar") %>%
  layout(yaxis = list(title = 'Mean Score'), barmode = 'stack', xaxis = list(title = 'Restaurant Name')) %>% 
  layout(title = "Average Inspection Scores for Each Restaurant on Amelia's List")
```





